Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-26 doc/manuscript/ESSDmanuscript.tex
reposition table
add in-prep note

@@

To transfer complete, reviewed ForC records into EFDB, we created R
scripts to restructure ForC records and populate EFDB's bulk import form
(``EFDB bulk import.xlsx''). Criteria for data transfer were that (1)
records had been checked against the original study and determined to be
complete and correct (\texttt{EFDB.ready} field in
\texttt{ForC\_citations} table), (2) the original study presented values
in tables or text, as opposed to the values having been digitized from
graphs or calculated based on related variables
(\texttt{data.location.within.source} field in
\texttt{ForC\_measurements} table), and (3) the records had not
previously been sent to EFDB. Once converted into EFDB format, the
records were reviewed and then sent to the IPCC's Technical Support Unit
for inclusion in EFDB. Complete records needed to be reviewed by the
EFDB editorial board prior to posting in the database -- a process that
lags behind records transfer and had not yet been completed for all
records sent as of April 22, 2022.

@@

As of April 22, 2022, ForC (v4.0) contained 32550 independent records
(39856 total), 17190 of which were for variables relevant to EFDB (Fig.
1). These records were distributed across all forested continents and
ecozones, with particularly high concentrations in
\emph{{[}ecozone(s){]}} and low concentrations in
\emph{{[}ecozone(s){]}} (Fig. 2). The most widely represented forest
type was \emph{{[}type{]}}, followed by \emph{{[}type{]}} and
\emph{{[}type{]}} (Fig. 3).

@@

As of April 22, 2022, we had reviewed or added 1985 EFDB-relevant
records, 1214 records of which were sent to EFDB, and 73 of which have
been reviewed, accepted, and posted (Figs. 2-3, Table 2).
\emph{{[}DETAILS{]}}

>>>>

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{THIS IS AN IN-PREP MANUSCRIPT.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

@@

To transfer complete, reviewed ForC records into EFDB, we created R
scripts to restructure ForC records and populate EFDB's bulk import form
(``EFDB bulk import.xlsx''). Criteria for data transfer were that (1)
records had been checked against the original study and determined to be
complete and correct (\texttt{EFDB.ready} field in
\texttt{ForC\_citations} table), (2) the original study presented values
in tables or text, as opposed to the values having been digitized from
graphs or calculated based on related variables
(\texttt{data.location.within.source} field in
\texttt{ForC\_measurements} table), and (3) the records had not
previously been sent to EFDB. Once converted into EFDB format, the
records were reviewed and then sent to the IPCC's Technical Support Unit
for inclusion in EFDB. Complete records needed to be reviewed by the
EFDB editorial board prior to posting in the database -- a process that
lags behind records transfer and had not yet been completed for all
records sent as of April 26, 2022.

@@

As of April 26, 2022, ForC (v4.0) contained 32550 independent records
(39856 total), 17190 of which were for variables relevant to EFDB (Fig.
1). These records were distributed across all forested continents and
ecozones, with particularly high concentrations in
\emph{{[}ecozone(s){]}} and low concentrations in
\emph{{[}ecozone(s){]}} (Fig. 2). The most widely represented forest
type was \emph{{[}type{]}}, followed by \emph{{[}type{]}} and
\emph{{[}type{]}} (Fig. 3).

@@

As of April 26, 2022, we had reviewed or added 1985 EFDB-relevant
records, 1214 records of which were sent to EFDB, and 73 of which have
been reviewed, accepted, and posted (Figs. 2-3, Table 2).
\emph{{[}DETAILS{]}}
